---
title: "Linear Model Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Model Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(BIOSTAT625HW3)
install.packages("bench")
require(bench)
```

How to use the `linearModel` function:

The `linearModel` function has 4 parameters:

`formula`: a formula object that specifies the form of the model to be fitted

`data`: a data frame containing the variables used in the formula for the linear model

`print.summary`: a Boolean indicator for printing a summary table of the function results


The following is an example of how to use the `linearModel` function. Here we will use the `iris` dataset from base R.

First, we will set up our parameters for input into the function for a simple linear regression (one predictor and one outcome).

```{r}
data("iris")

form <- as.formula(Sepal.Length ~ Petal.Length)

```


We then run the `linearModel`function with the defined parameters. We save the results to a variable named lm1. Here we specify `print.summary = FALSE`, so the summary table is not printed.

```{r}
lm1 <- linearModel(formula = form, data = iris, print.summary = FALSE)
```

Here is an example of using `print.summary = TRUE`. This summary is of similar format to the output from the `lm` function.

```{r}
lm1 <- linearModel(formula = form, data = iris, print.summary = TRUE)
```


The `linearModel` function returns a list containing coefficients, residuals, and fitted values from the specified linear model, as well as the values from the summary table.

```{r}
lm1
```


Next, we will run a multiple linear regression model using the `linearModel` function and the same data set.

```{r}
data("iris")

form <- as.formula(Sepal.Length ~ Sepal.Width + Petal.Width + Petal.Length + Species)

```


We will run the function with `print.summary = TRUE` to show the summary output. 

```{r}
lm2 <- linearModel(formula = form, data = iris, print.summary = TRUE)
```


To check the accuracy of our results, we will compare the output of our model to the `lm` function.

```{r}
lmtest <- lm(form, data = iris)
all.equal(as.numeric(lmtest$coefficients), as.numeric(lm2$coefficients))
all.equal(as.numeric(lmtest$residuals), as.numeric(lm2$residuals))
all.equal(as.numeric(lmtest$fitted.values), as.numeric(lm2$fitted.values))

#comparing summary tables
summary(lmtest)
lm2 <- linearModel(formula = form, data = iris, print.summary = TRUE)
```

We will also check the efficiency of our function compared to the `lm` function.

```{r}
bench::mark(as.numeric(lm(form, data = iris)$coefficients), as.numeric(linearModel(formula = form, data = iris, print.summary = FALSE)$coefficients))
```



